\documentclass[a4paper,nocourse]{miunasgn}
\usepackage[utf8]{inputenc}
\usepackage[swedish,english]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{prettyref,varioref}
\usepackage[today,nofancy]{svninfo}
\usepackage[natbib,style=numeric-comp,maxbibnames=99,sorting=none,backend=bibtexu]{biblatex}
\addbibresource{literature.bib}
\usepackage[varioref,prettyref]{miunmisc}

\svnInfo $Id$

\courseid{DT116G}
\course{Network Security}
\assignmenttype{Seminar}
\title{Ethics in network security}
\author{Daniel Bosk\\
  {\small\href{mailto:daniel.bosk@miun.se}{daniel.bosk@miun.se}}
  \and
  Lennart Franked\\
  {\small\href{mailto:daniel.bosk@miun.se}{lennart.franked@miun.se}}
}
\date{\svnId}

\begin{document}
\maketitle
\thispagestyle{foot}
\tableofcontents

\section{Aims}
The aim of this assignment is to
\begin{itemize}
    \input{aims.tex}
\end{itemize}


\section{Reading instructions}
\label{sec:Reading}
\input{literature.tex}


\section{Tasks}
\label{sec:Tasks}
Select one of the topics listed below and reflect on the
ethical implications.
\begin{itemize}
  \item Face-recognition in enormous databases, like those of Google or
    Facebook.

  \item Accessing sensitive information in closed systems (patient journals,
    bank transactions records et cetera).

  \item Trackable banknotes.

  \item Performing wiretapping ordered by a company or government.

  \item Publishing information about other people's activity on Facebook or
    Twitter (this covers everything from tagging a person in a picture
    on Facebook, Twittering about visiting that person, to publishing
    sensitive information).

  \item As an operator storing and logging all activity in a phone or computer 
    network.

  \item As a person having knowledge of secret Internet surveillance 
    programmes, e.g.\ like Edward Snowden 
    \cite{landau2013snowden,landau2014highlights}.
\end{itemize}


\section{Examination}
\label{sec:Examination}
This assignment is examined through active participation in a seminar.
To prepare for this seminar you must write your discussion in a PM.
The title page on your PM shall only contain the following information:
\begin{itemize}
  \item The author's full name and email address.
  \item A suitable title that also contains the name of the assignment, e.g.\ 
    \emph{Seminar on ethics in network security: Ethics regarding trackable 
    banknotes}.
  \item A 200--300 word abstract of your PM.
\end{itemize}

The pages that follows shall follow the instructions given in 
\prettyref{sec:Tasks}.
Your text must contain clear citations based on the Vancouver system. 

The scope of the PM shall be at least 1500 words, abstract not included.

This PM shall then be posted in the course platform and be read by another 
student, and of course you should then read another student's PM.
You must therefore publish your PM in the course platform at the latest a week 
before the seminar!


\printbibliography
\end{document}
