\title{%
  What's up with security?
}
\author{Daniel Bosk}
\institute{%
  KTH EECS
  \and
  MIUN IST
}

\mode<article>{\maketitle}
\mode<presentation>{%
  \begin{frame}
    \maketitle
  \end{frame}
}

\mode*

\begin{abstract}
  \input{abstract.tex}
\end{abstract}


\section<article>{Introduction}

Our world becomes increasingly dependent on computer systems, it is thus 
important that those who can affect these systems do that in a responsible 
way.
But what is a responsible way, what are the limits?
This is the topic of ethics, the reasoning about moral obligations.
The purpose of this seminar is to discuss what those responsibilities are and 
where the limits are.

%There are various examples that illustrate the problems caused by lacking 
%security.
%For example, since our digital world allows the copying of information more 
%easily, more people do this.
%This can happen in the form of people using a service for publishing 
%photographs to friends, or to the entire world for that matter.
%Even this innocuous activity can cause problems:
%for instance, when a child posted vacation pictures to 
%Instagram~\cite{Roberts2012wia}.
%This happened to be not any child, it reached the news only because the child 
%was a member of the Norwegian royal family.
%These images posted, did due to our technical development, contain the exact 
%GPS coordinates of the location where the picture was taken.
%The result was that the position of the royal family was published in almost 
%real-time, information which is normally strictly secret.
%However, this is also an issue for non-celebrities: a family was robbed in 
%their house due to a sales advertisement~\cite{BlocketRobbery}.


\section{Aims}

This seminar aims for reflection of how security, or lack thereof, affects 
products, people, society and discuss the responsibilities of engineers.
\begin{frame}
After doing this assignment your should be able:
\begin{itemize}
  \item to \emph{reflect} on the effects of security, or lack thereof, on both 
    individual and society.
  \item to \emph{value and argue} about the responsibilities of engineers.
\end{itemize}
\end{frame}


\section{Assignment}%
\label{sec:Tasks}

\mode<presentation>{\subsection{Influence campaigns}}

Read up on the influence campaigns during the 2016 US 
election~\cite{inside-russian-influence-campaign}.
Focus on the reliance on technologies:
\begin{frame}
  \mode<presentation>{%
    References:
    \begin{itemize}
      \item \fullcite{inside-russian-influence-campaign}
    \end{itemize}

    \begin{question}
  }
  \begin{itemize}
    \item Which technologies were used?
    \item Were they used correctly or \enquote{hacked}?
    \item What allowed this to happen?
    \item \Etc
  \end{itemize}
\mode<presentation>{\end{question}}
\end{frame}

\mode<presentation>{\subsection{Cambridge Analytica and Mirai}}

Then you must read up on the Cambridge Analytica scandal~\cite[\eg][]{%
  wired-cambridge-analytica,
  guardian-cambridge-analytica,
  nytimes-cambridge-analytica,
  wp-cambridge-analytica,
} and the Mirai botnet incident~\cite{schneier-mirai}.
Search for some more news articles about security and how bad security can have 
negative effects on a societal scale:
\mode<presentation>{%
  \begin{frame}
    References:
    \begin{itemize}
      \item Wired: \citetitle{wired-cambridge-analytica},
      \item Guardian: \citetitle{guardian-cambridge-analytica},
      \item NYT: \citetitle{nytimes-cambridge-analytica},
      \item WP: \citetitle{wp-cambridge-analytica}, and
      \item \citetitle{schneier-mirai}
    \end{itemize}
  \end{frame}
}
\begin{frame}
  \mode<presentation>{\begin{question}}
\begin{itemize}
  \item What are the consequences of this weak security, what other effects can 
    this have on society?
  \item Give other examples.
\end{itemize}
\mode<presentation>{\end{question}}
\end{frame}

\mode<presentation>{\subsection{Codes of ethics}}

\mode<presentation>{%
  \begin{frame}
    References:
    \begin{itemize}
      \item \citetitle{acmcode},
      \item \citetitle{acmsecode},
      \item \citetitle{ieeecode}.
    \end{itemize}
  \end{frame}
}
Use the codes of ethics~\cite{acmcode,acmsecode,ieeecode} as a base to reflect 
on the questions:
\begin{frame}
  \mode<presentation>{\begin{question}}
\begin{itemize}
  \item Where does the responsibility of the engineers who contributed to these 
    systems end?
  \item Should they be morally obliged to ensure the user can make an informed 
    choice?
  \item Or is that totally the responsibility of the user?
  \item What if the design does not let the user make an informed choice?
  \item What if the design intentionally deceives the user to make the 
    \enquote{wrong} choice?
  \item If there is no regulation in law, is anything allowed?
\end{itemize}
\mode<presentation>{\end{question}}
\end{frame}

Do not limit yourself to this exact set of questions (for all three parts), 
explore further.
Write down your thoughts (reasoning, discussion \etc), that will be valuable 
support later.

Work in groups, discuss each others' thoughts, the newfound news articles and 
summarize the discussions in documented form (on paper, as a presentation, 
\etc, this is to support yourself).


\section{Assessment}%
\label{Assessment}

This assignment is assessed through active participation in a seminar.
To prepare for this seminar, follow the instructions in \cref{sec:Tasks}.
You must participate actively to pass this assessment.

The structure of the seminar will be as follows:
\begin{enumerate}
  \item We will divide the class into smaller groups (randomly), so not the 
    working groups.
    We want to learn any insights from other groups.

  \item Each person in this random group present the conclusions from above, 
    some of the more interesting news articles that you found.
    Then discuss these conclusions and any differences.
    In case of similar conclusions, you can see if you arrived at the same 
    conclusion by similar reasoning or not.
    (We will allocate 45 minutes to this, including a short break, 10--15 
    minutes.)

  \item Finally, we will summarize your experiences together in full class.
    We will particularly aim for the question: what were the major 
    differences, similarities, and what responsibility will you have as 
    engineers?
    (This will take around 20--30 minutes.)
\end{enumerate}

\mode<presentation>{%
\begin{frame}
  \begin{enumerate}
    \item Divide into groups randomly.

    \item Group discussions, 45 minutes including 10--15 minutes break:
      \begin{itemize}
        \item Each person presents group's reasoning and conclusions to the 
          random group.
        \item Discuss differences, similarities \etc.
      \end{itemize}

    \item Summarize in full class.
  \end{enumerate}
\end{frame}

\begin{frame}
  \begin{question}
    \begin{itemize}
      \item What were the major differences, similarities in opinions?
    \end{itemize}
  \end{question}

  \begin{question}
    \begin{itemize}
      \item What responsibility will you have as engineers?
    \end{itemize}
  \end{question}
\end{frame}
}


%%% REFERENCES %%%

\begin{frame}[allowframebreaks]
  \printbibliography{}
\end{frame}
